### 2020-02-26 README.Rmd
updated readme

The lower-level fuinctionm

The functions `zb_doughnuts` generates rings:

@@

```{r}
tmap_arrange(
  qtm(zb_zone(london_area, london_cent, n_segments = 1, n_circles = 5), title = "Doughnuts") + tmap_border,
  qtm(zb_zone(london_area, london_cent, n_segments = 12, n_circles = 1, segment_center = TRUE), title = "Segments") + tmap_border,
  qtm(zb_quadrat(london_area, london_cent, ncol = 4), title = "Quadrants") + tmap_border
)
```

>>>>

The function `zb_zone` makes use of `zb_doughnut` and `zb_segment`, which can also be used directly:

@@

However, if the zones should be intersected with the administrative area, `zb_zone` can be used as follows:

```{r}
tmap_arrange(
  qtm(zb_zone(london_area, london_cent, n_segments = 1), title = "Doughnuts") + tmap_border,
  qtm(zb_zone(london_area, london_cent, n_segments = 12, n_circles = 1, distance = 30, segment_center = TRUE), title = "Segments") + tmap_border
)
```

Finally, another zoning system that is implemented in `zonebuilder` is:

```{r}
  qtm(zb_quadrat(london_area, london_cent, ncol = 4), title = "Quadrants") + tmap_border
```
